Fast Sorting on Modern Computers

### 2005-05-27 paper/docs/background.tex
make way for the new and improved fs
removed files not for paper removed extra bits

A \n{stable} sort is one in which records which have the same key stay in the
same order across the sort. All the elementary sorts are stable, as is
mergesort, heapsort and radixsort. Quicksort is not stable.

@@

The address used by the cache is not necessarily the address used by a program.
The addresses used within a program 
are called \n{virtual addresses}. Some caches are addressed by virtual address,
some caches by \n{physical address}, and some caches by \n{bus
address}\footnote{A bus address is used to address parts of the computer
connected over a bus, including main memory, multimedia controllers such as
sound and graphics cards, and storage devices such as hard drivers and floppy
disk controllers.}. Several optimisations in later chapters use the address to
offset arrays so that conflicts are not caused. However, because a program
cannot be sure of what type of addressing is used, the actual manipulated
address may not directly relate to the index used to address the cache. This
problem is not encountered in simulations in this project, as SimpleScalar
addresses its caches by virtual address.

>>>>

A \n{stable} sort is one in which records which have the same key stay in the
same order across the sort. All the elementary sorts are stable, as are
mergesort and radixsort. Quicksort, heapsort and shellsort are not stable.

@@

The address used by the cache is not necessarily the address used by a program.
The addresses used within a program 
are called \n{virtual addresses}. Some caches are addressed by virtual address,
some caches by \n{physical address}, and some caches by \n{bus
address}\footnote{A bus address is used to address parts of the computer
connected over a bus, including main memory, multimedia controllers such as
sound and graphics cards, and storage devices such as hard drivers and floppy
disk controllers.}. Several optimizations in later chapters use the address to
offset arrays so that conflicts are not caused. However, because a program
cannot be sure of what type of addressing is used, the actual manipulated
address may not directly relate to the index used to address the cache. This
problem is not encountered in simulations in this project, as SimpleScalar
addresses its caches by virtual address.

### 2005-05-27 paper/docs/report.tex
removed files not for paper removed extra bits

\title{Fast Sorting on Modern Computers}
\author{Paul Biggar\\ B.A. (Mod.) Computer Science \\ Final Year Project April 2004 \\ Supervisor: Dr. David Gregg}
\date{}

@@

\begin{titlepage}
        \begin{center}
                \vspace*{95mm}
                \LARGE Fast Sorting on Modern Computers\\
                \vspace{1em}
                \large Paul Biggar\\
                \large B.A. (Mod.) Computer Science \\
                \large Final Year Project April 2004\\
                \large Supervisor: Dr. David Gregg\\
        \end{center}
\end{titlepage}

@@

\chapter*{Declaration}

I hereby declare that this thesis is entirely my own work and that it has not
been submitted as an exercise for a degree at any other university.

\begin{center}
\vspace*{2in}

\underline{\hspace*{3in}} \today

Paul Biggar
\end{center}

\chapter*{Acknowledgments}
I would like to thank my supervisor, Dr. David Gregg, for his help and advice
during this project. I'd also like to thank those who read my first draft, and
my friends and family for their support during the last year, and my entire time
at college. Thank you.
\newpage

@@

%\chapter{Software Predictor Result Listing}
%\input software_predictor.tex

\chapter{Code Listing}
\input code_list.tex

% the bugs are now fixed (actually, one of them was only mistakenly a bg :)
% the only remaining thing is the compulsory cache subtraction.
\chapter{Bug List}
\input bugs.tex

\chapter{SimpleScalar installation}
\input simplescalar.tex

>>>>

\title{Fast Sorting on Modern Computers}
\author{Paul Biggar, David Gregg}
\date{}

@@

@@

@@

%TODO \chapter{Software Predictor Result Listing}
%\input software_predictor.tex

% TODO the bugs are now fixed (actually, one of them was only mistakenly a bg :)
% the only remaining thing is the compulsory cache subtraction.
\chapter{Bug List}
\input bugs.tex
